% Dr. Geoff Boeing - Curriculum Vitae
% Copyright 2018 Geoff Boeing
% Email: g.boeing@northeastern.edu
% Web: https://geoffboeing.com/

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) so accented characters are a single glyph
\usepackage[utf8]{inputenc} % allow input of utf-8 encoded characters
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % automatically regionalize hyphens, quote marks, etc
\usepackage{microtype} % improves text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto} % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts

% what is your name?
\newcommand{\myname}{Yuxin Tang}

% define a default font face and set it as the body font
\usepackage{crimson} % document's serif font
\usepackage{helvet}  % document's sans serif font

% define how far to tab for list items with left-aligned date - different font faces need different widths
\newcommand{\listtabwidth}{2.75cm}

% set name font to title the document
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*}{6}
\titleformat{\section}{\sffamily\small\bfseries\lsstyle\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{10pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{6pt plus 4pt minus 2pt}{8pt plus 2pt minus 2pt}

% set page margins
\geometry{body={6.5in, 9.0in},
	left=1.0in,
	top=1.0in}

% prevent paragraph indentation
\setlength\parindent{1em}

% define space between list items
\newcommand{\listitemspace}{0.05em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
			\setlength{\parskip}{0em}
			\setlength{\itemsep}{\listitemspace}
			\setlength{\parsep}{\listitemspace}}}
	{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
	labelindent=0em,
	topsep=0em,
	partopsep=0em,
	itemsep=\listitemspace,
	parsep=\listitemspace,
	font=\normalfont}

% print the month and year only when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
	colorlinks = true,
	urlcolor = black,
	pdfauthor = {\myname},
	pdfkeywords = {city planning, urban design, spatial data science, street networks, housing},
	pdftitle = {\myname: Curriculum Vitae},
	pdfsubject = {Curriculum Vitae},
	pdfpagemode = UseNone
}

\begin{document}
	\raggedright
	
	% display name as the document title
	\namefont{\myname}
	
	% contact info
	\vspace{1em}
	\begin{minipage}[t]{0.495\textwidth}
		Department of Computer Science \\
		Rice University \\
		Houston, Texas
	\end{minipage}
	\begin{minipage}[t]{0.495\textwidth}
		Email: yuxin.tang@rice.edu \\
		Phone: +1 713 560 6850
	\end{minipage}
	\vspace{0.5em}

	\section*{Skills}
	
	\subsection*{Programming}
	
	\begin{itemize}
		\item - Python, C++, CUDA. 
		\item - Expertise with deep learning system performance optimization
	\end{itemize}
	
	\subsection*{Framework}
	
	\begin{itemize}
		\item - PyTorch, PostgreSQL, Spark, Flutter, MongoDB, Android/iOS
		\item - Familiar with machine learning system design and database system design
	\end{itemize}	
	
	\section*{Education}
	
	\begin{tablist}
		\item[Ph.D.] \tab Computer Science, Rice University, 2018-Present \\
		Advisor: Chris Jermaine\\
		%Committee: Paul Waddell (chair), Robert Cervero, Elizabeth Macdonald, David O'Sullivan
		\item[B.S.]  \tab Computer Science, Shanghai Jiao Tong University, 2014-2018
	\end{tablist}

	\section*{Research Areas}

    \begin{itemize}
        \item Large-scale machine learning, data management for machine learning
		\item Distributed machine learning, on-device machine learning, federated learning
    \end{itemize}

	\section*{Internship}
	
	\begin{tablist}
		\item[2022] \tab ByteDance Inc, Mountain View, CA \\
		Graph Learning Team - Applied Research Center\\
		\begin{itemize}
			\item - Worked on self-supervised learning (SSL) on graphs and implemented the multi-view graph contrastive learning model (MVGRL) on large graph datasets. 
			\item - Worked on the scalability issues of graph diffusion by approximating personalized PageRank. End-to-end training time is reduced 60\%.
			\item - Worked on the sparse tensor representation for graph preprocessing, graph training and inference. Peak memory usage is reduced to only 29\%.
		\end{itemize}
		\item[2018] \tab Pygmal Technologies, Shanghai \\
		\begin{itemize}
			\item - Formalized one cryptocurrency trading platform front-end design 
			\item - Developed one cryptocurrency trading platform mobile application using Flutter 2.0
		\end{itemize}
		\item[2017-2018] \tab Intel Asia-Pacific Research \& Development Ltd, Shanghai \\
		Javascript Technology Center\\
		\begin{itemize}
			\item - Improved average page load speed by around 5\% for JavaScript engine in Chrome V8
			\item - Submitted 10 more patches for Chromium Speedometer 2.0 benchmark
			\item - Identified possible performance optimization for web-assembly (wasm) opencv.js benchmark by JIT compilation
		\end{itemize}
	\end{tablist}

%	\section*{Projects}
	
%	\begin{tablist}
%		\item[2021] \tab Scaling Graph Neural Network with RDBMS \\
%		\begin{itemize}
%			\item - Implemented Graph Convolutional Neural Network in PlinyCompute
%			\item - Scaled distributed GCN training to large graph with billion edges in less than 1h
%			\item - Improved message passing throughput by around 10\% by graph partitioning 
%		\end{itemize}
%		\item[2020] \tab Federated Learning with Independent Subnet Training \\
%		\begin{itemize}
%			\item - Implemented simulation of federated learning by tensor partition
%			\item - Improved SOTA accuracy on MNIST and CIFAR-10 datasets
%		\end{itemize}
%		\item[2020] \tab Federated Learning for Extreme Classification \\
%		\begin{itemize}
%			\item - Implemented FedMLH using PyTorch and OpenMP
%			\item - Constructed benchmarks with Non-IID extreme classification datasets  
%			\item - Analyzed around 5\% classification accuracy gain with FedAvg and FedProx
%		\end{itemize}
%		\item[2019-2020] \tab GPU accelerated Distributed Big Data System \\
%		\begin{itemize}
%			\item - Implemented GPU Buffer Pool for parameter swapping and caching
%			\item - Implemented CUDAStreams binding for asynchronous data transfer prefetching
%			\item - Optimized Join and Aggregation operators by building another level of indirection of raw pointers.
%		\end{itemize}
%	\end{tablist}
	
	\section*{Publication}
	\begin{tablist}
		\item[2023] \tab \textbf{Auto-Differentiation of Database Queries for Very Large Scale
		Machine Learning.}
		\\\underline{Yuxin Tang}, Zhimin Ding, Dimitrije Jankov, Binhang Yuan, Daniel Bourgeois, Chris Jermaine.
		\\\textit{In submission.}
		\item[2022] \tab \textbf{Distributed learning of fully connected neural networks using independent subnet training.} 
		\\Binhang Yuan, Cameron R. Wolfe, Chen Dun, \underline{Yuxin Tang}, Anastasios Kyrillidis, Chris Jermaine.
		\\\textit{VLDB'22} 
		\item[2021] \tab \textbf{Federated Multiple Label Hashing (FedMLH): Communication Efficient Federated Learning on Extreme Classification Tasks.} 
		\\ \underline{Yuxin Tang}, Zhenwei Dai, Chen Dun, Anastasios Kyrillidis, Anshumali Shrivastava.
		\\ \textit{ICML-FL'21}
		\item[2021] \tab  \textbf{Tensor Relational Algebra for Machine Learning System Design.} 
		\\Binhang Yuan, Dimitrije Jankov, Jia Zou, \underline{Yuxin Tang}, Daniel Bourgeois, and Chris Jermaine.
		\\\textit{VLDB'21}
		\item[2020] \tab \textbf{Programmable In-Network Security for Context-aware BYOD
		Policies.}
		\\Qiao Kang, Lei Xue, Adam Morrison, \underline{Yuxin Tang}, Ang Chen, Xiapu Luo.
		\\\textit{USENIX Security'20}
		\item[2018] \tab \textbf{A Programmable, Hardware-Assisted Network Protocol Fuzzer.}
		\\\underline{Yuxin Tang}, Ang Chen.
		\\\textit{OSDI'18} 
		\item[2017] \tab \textbf{Exploring Simulation of Software-Defined Underwater Wireless Networks.} 
		\\Li Wei, \underline{Yuxin Tang}, Yuching Cao, Zhaohui Wang, Mario Gerla.
		\\\textit{MobiCom'17 Workshop on Underwater Networks}
	\end{tablist}
	
	\section*{Awards}

	\begin{tablist}
		
		\item[2022] \tab ICML travel grant

		\item[2020] \tab Ken Kennedy Institute Computational Science and Engineering Fellowship (\$15,000/4 years)
				
		\item[2017] \tab Hongyi Scholarship (¥25,000)
		
		\item[2016] \tab Gold Medal, International Genetically Engineered Machine Competition
		
		\item[2015] \tab Chun-Tsung Scholar (funded by Nobel Prize Winner T. D. Lee) (¥15,000)
		
		\item[2014] \tab Scholarship of Academic Excellence of SJTU

	\end{tablist}	

	\section*{Service}
    \begin{itemize}
        \item Conference Reviewer: 
		\\ \textit{ICML 2021}, \textit{ICML 2022}, \textit{NeurIPS 2022}, \textit{AISTATS 2023}
    \end{itemize}
\end{document}
